---
title: "Restaurant Inspections in Queens (2011-2017)"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r include = FALSE,message=FALSE,warning=FALSE}
library(flexdashboard)
library(tidyverse)
library(httr)
library(p8105.datasets)
library(jsonlite)
library(plotly)
library(ggpubr)
library(stringr)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

```{r, message = FALSE, echo = FALSE, include=FALSE}
data("rest_inspec")

nyc_inspections_df <- rest_inspec |> 
  mutate(boro = str_to_title(boro), 
         critical_flag = case_when(critical_flag == "Not Applicable" ~ NA, 
                          TRUE ~ critical_flag), 
         inspection_date = case_when(inspection_date < 2011 ~ NA, 
                          TRUE ~ inspection_date),
         score = as.numeric(score), 
         inspection_date = as.Date(inspection_date), 
         year = as.factor(year(inspection_date))) |> 
  filter(boro == "Queens") |> 
  drop_na(inspection_date)
```

column {data-width=500}
-----------------------------------------------------------------------

### Chart A: Number of code violations registered per restaturant

```{r, echo = FALSE, warnin = FALSE, message = FALSE, fig.height=15}
number_of_inspection <- 
  nyc_inspections_df |> 
  count(camis, year) |> 
  ggplot(aes(x = year, y = n)) +
  geom_boxplot() +
  labs(y = "Number of Violations per Restuarant", 
       x = "Year")

ggplotly(number_of_inspection)
```

> The average number of code violations for each restaurant remained below five at each year. However, during the later years, particularly in 2015, there were some restaurants who had large number of violations. 

### Chart B: Critical and Non-critical Violations
```{r, echo = FALSE, fig.height=5}
critical_flag_cat <- 
  nyc_inspections_df |> 
  drop_na(critical_flag) |> 
  group_by(critical_flag, camis) |> 
  summarize(n_violations = n()) |> 
  group_by(camis) |> 
  mutate(difference = (n_violations[2] - n_violations[1]), 
         color = case_when(difference > 0 ~ "increase", 
                           difference <= 0 ~ "decrease")) |> 
  #mutate(critical_flag = forcats::fct_reorder(critical_flag, score, .na_rm = TRUE)) |> 
  ggplot(aes(x = critical_flag, y = n_violations, color = color, group = camis)) + 
  geom_path(linewidth = 0.5, alpha = 0.5)+
  geom_point(size = 0.5) +
  labs(y = "Count (in 10 years)", 
       x = "Type of Violations per Restaurant", color = "") +
  scale_color_manual(values = c("#CC6666","#9999CC")) +
  theme_classic()

ggplotly(critical_flag_cat)
```

> In the 7 years, restaurants have had a comparable number of both critical and non-critical violations. However, in most cases, they seem to have more critical violations registered than the non-critical ones. Missing values are those who either only have critical or only non-critical violations. 

Column {data-width=500}
-----------------------------------------------------------------------

### Chart C: Is there an association between number of inspections and violation score (2014_2017)?

```{r, echo = FALSE, warning = FALSE}
scatter_plot <- nyc_inspections_df |> 
  filter(year %in% c(2014, 2015, 2016, 2017)) |> 
  group_by(inspection_date, camis, dba, year, cuisine_description) |> 
  summarize(score = score[1]) |> 
  group_by(cuisine_description, year) |> 
  summarize(number_of_restaurants = length(unique(camis)), 
            average_score = mean(score, na.rm = TRUE), 
            average_number_of_inspections = n()/number_of_restaurants) |> 
  mutate(name = str_to_title(cuisine_description)) |> 
  ungroup() 

scatter_plot <-  
  scatter_plot |> 
  ggplot(aes(x = average_number_of_inspections, y = average_score, label = name)) +
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = lm, se = FALSE, linewidth = 0.5) +
  ggpubr::stat_cor(method = "pearson", label.x = 2.2, label.y = max(scatter_plot$average_score, na.rm = T), output.type= "text") +
  labs(y = "Average Violation Score", 
       x = "Average Number of Inspection", 
       color = "Violation Types") +
  facet_wrap(~year, ncol = 2)

ggplotly(scatter_plot)
```

> In the later years, cuisines whose restaurants were found to violate more/critical City and State food safety requirements also received more inspections during the year. Many of the inspections could be follow-ups. Similarly, it could also be that restuarants who are inspected more are likely to have more violations recorded.  



